---
title: "R Notebook"
output: html_notebook
---
# no 2000

```{r}
library(dtwclust)
library(dtw)
```



```{r}
df<-read.csv("../clean_data/gap_list_year.csv")
df
```
```{r}
df <- subset(df, select = -c(X) )
df
```

```{r}
colnames(df)[colnames(df) == "X2002"] = "2002"
colnames(df)[colnames(df) == "X2003"] = "2003"
colnames(df)[colnames(df) == "X2005"] = "2005"
colnames(df)[colnames(df) == "X2007"] = "2007"
colnames(df)[colnames(df) == "X2009"] = "2009"
colnames(df)[colnames(df) == "X2011"] = "2011"
colnames(df)[colnames(df) == "X2013"] = "2013"
colnames(df)[colnames(df) == "X2015"] = "2015"
colnames(df)[colnames(df) == "X2017"] = "2017"
colnames(df)[colnames(df) == "X2019"] = "2019"
colnames(df)[colnames(df) == "X2022"] = "2022"
```
```{r}
df
```


```{r}
jurisdiction = df[['Jurisdiction']]
```
```{r}
dtw_df <- df[, -1]
```


```{r}
dtw_df
```


```{r}
df_lst <- tslist(dtw_df)
```
```{r}
remove_nan <- function(ts) {
  ts[!is.na(ts)]
}

# Apply the function to each time series in the list
df_lst <- lapply(df_lst, remove_nan)
```
```{r}
head(df_lst)
```

## index score evaluation

```{r}
df_cvi <- list()
for (i in 2:10){
  df_clust <- tsclust(df_lst, type = "partitional", k = i, distance = "dtw_basic", centroid = "pam")
  df_metric <- cvi(df_clust, type = "valid", log.base = 10)
  df_cvi <- append(df_cvi, list(df_metric))
}
```

```{r}
df_cvi_ma <- do.call(rbind, df_cvi)
rw <- c("K2","K3","K4","K5","K6","K7","K8","K9","K10")
rownames(df_cvi_ma) <- rw
print(df_cvi_ma)
```
– "Sil" (!): Silhouette index (Rousseeuw (1987); to be maximized).-K4
– "SF" (~): Score Function (Saitta et al. (2007); to be maximized; see notes).
– "CH" (~): Calinski-Harabasz index (Arbelaitz et al. (2013); to be maximized).-k3
– "DB" (?): Davies-Bouldin index (Arbelaitz et al. (2013); to be minimized).k4
– "DBstar" (?): Modified Davies-Bouldin index (DB*) (Kim and Ramakrishna (2005); to be minimized). -k4
– "D" (!): Dunn index (Arbelaitz et al. (2013); to be maximized). k5
– "COP" (!): COP index (Arbelaitz et al. (2013); to be minimized). k9

# different seeds index score result

```{r}
df_cvi2 <- list()
for (i in 1:100){
  df_clust2 <- tsclust(df_lst, type = "partitional", k = 4, distance = "dtw_basic", centroid = "pam", seed=i)
  df_metric2 <- cvi(df_clust2, type = "valid", log.base = 10)
  df_cvi2 <- append(df_cvi2, list(df_metric2))
}
df_cvi_ma2 <- do.call(rbind, df_cvi2)
rw2 <- as.character(seq(1, 100))
rownames(df_cvi_ma2) <- rw2
print(df_cvi_ma2)
```

## Cluster evaluation

```{r}
for (i in 2:10){df_clust_opt <- tsclust(df_lst, type = "partitional", k = i, distance = "dtw", centroid = "pam",seed = 725)
plot(df_clust_opt)}
```


## Seeds Evaluation

```{r}
for (i in 1:10){df_clust_opt_final <- tsclust(df_lst, type = "partitional", k = 4, distance = "dtw", centroid = "pam",seed = i)
plot(df_clust_opt_final)}
```
```{r}
# for (i in 11:20){df_clust_opt_final <- tsclust(df_lst, type = "partitional", k = 4, distance = "dtw", centroid = "pam",seed = i)
# plot(df_clust_opt_final)}
```


## We using cluster=4
```{r}
#k4
df_clust_opt_final <- tsclust(df_lst, type = "partitional", k = 4, distance = "dtw", centroid = "pam",seed = 5)
plot(df_clust_opt_final)
```

## Plot detailed clusters
```{r}
# Extract cluster assignments
cluster_assignments <- df_clust_opt_final@cluster

# Determine the number of clusters
num_clusters <- max(cluster_assignments)

# Loop through each cluster and print the jurisdictions in it
for (cluster_number in 1:num_clusters) {
  cat("Jurisdictions in Cluster", cluster_number, ":\n")
  
  # Find the indices of jurisdictions in this cluster
  indices_in_cluster <- which(cluster_assignments == cluster_number)
  
  # Print the jurisdictions corresponding to these indices
  print(jurisdiction[indices_in_cluster])
  
  cat("\n") # Add a newline for readability
}
```
```{r}
# Create an empty dataframe to store the results
jurisdiction_clusters <- data.frame(Jurisdiction = character(), G8_Cluster = numeric(), stringsAsFactors = FALSE)

# Loop through each cluster and append the jurisdictions and their cluster number to the dataframe
for (cluster_number in 1:num_clusters) {
  # Find the indices of jurisdictions in this cluster
  indices_in_cluster <- which(cluster_assignments == cluster_number)
  
  # Extract the jurisdictions corresponding to these indices
  jurisdictions_in_cluster <- jurisdiction[indices_in_cluster]
  
  # Create a temporary dataframe for this cluster
  temp_df <- data.frame(Jurisdiction = jurisdictions_in_cluster, G8_Cluster = rep(cluster_number, length(jurisdictions_in_cluster)), stringsAsFactors = FALSE)
  
  # Append the temporary dataframe to the main dataframe
  jurisdiction_clusters <- rbind(jurisdiction_clusters, temp_df)
}

# Export the dataframe to a CSV file
write.csv(jurisdiction_clusters, "../clean_data/jurisdiction_clusters_G8.csv", row.names = FALSE)
# View the resulting dataframe
print(jurisdiction_clusters)
```


```{r}
# Load necessary libraries
library(ggplot2)
library(reshape2)

# Loop through each cluster
for (cluster_number in 1:num_clusters) {
  cat("Plotting jurisdictions in Cluster", cluster_number, ":\n")
  
  # Find the indices of jurisdictions in this cluster
  indices_in_cluster <- which(cluster_assignments == cluster_number)
  
  # Get the names of the jurisdictions in this cluster
  jurisdictions_in_cluster <- jurisdiction[indices_in_cluster]
  
  # Filter the gap_list_year data frame for these jurisdictions
  cluster_data <- df[df$Jurisdiction %in% jurisdictions_in_cluster, ]
  
  # Convert the data to long format for ggplot
  long_df <- melt(cluster_data, id.vars = "Jurisdiction", variable.name = "Year", value.name = "Value")
  
  # Plot
  p <- ggplot(long_df, aes(x = Year, y = Value, group = Jurisdiction, color = Jurisdiction)) +
    geom_line() +
    labs(title = paste("Cluster", cluster_number), x = "Year", y = "Gap") +
    theme(legend.position = "right")
  
  print(p)

  #ggsave(paste("cluster_", cluster_number, ".png", sep=""), plot = p)
}
```

